### 2015-11-19 Irregular-occ/Irregular-occ.tex
.

\begin{figure*}
\subfigure{\includegraphics[width=8.8cm]{Laurene/residuals/Himalia_resid.eps}   \label{Fig: residuals-Himalia}}
\subfigure{\includegraphics[width=8.8cm]{Laurene/residuals/Carme_resid.eps}  \label{Fig: residuals-Carme}}
\caption{Residuals of Himalia and Carme \label{Fig: residuals}}
\end{figure*}

@@

\begin{table*}
\caption{\label{Tab: sample-cds} Stellar occultation sampled predictions for Himalia \textcolor{red}{I still have to fix the table}}
\begin{centering}
\begin{tabular}{l}
\hline 
%\multicolumn{9}{c}{Himalia} \tabularnewline
\hline
% & \multicolumn{2}{c}{Mean errors} & Nr & Nr &  UCAC4       \tabularnewline

\hline
\end{tabular}
\par\end{centering}
\textbf{Notes}. Entries included: day of the year and UTC time of the prediction; right ascension and declination of the occulted star - in the original table, these coordinates are immediately followed by the geocentric astrometric equatorial coordinates of the satellite (corrected the computed ephemeris offset derived in Sec. \ref{Sec: integration}); C/A: the geocentric closest approach, in arcseconds; P/A: the planet position angle with respect to the occulted star at C/A, in degrees; velocity in plane of sky, in km s$^{-1}$: positive = prograde, negative = retrograde; D: planet range to Earth, in AU; R*: normalized magnitude to a common shadow velocity of 20 km s$^{-1}$ by the relationship $\textrm{Mag}* = \textrm{Mag}_{\textrm{actual}} + 2.5 \times \log 10 \left(\frac{\textrm{velocity}} {20 \textrm{km}\, \textrm{s}^{-1}} \right)$. A value of 50.0 means that the star is not in the 2MASS; $\lambda$: east longitude of subplanet point in degrees, positive towards east; LST: UT + $\lambda$: local solar time at subplanet point, hh:mm; $\Delta e_{\alpha *}$ and $\Delta e_{\delta}$: computed offsets in mas applied to the ephemeris right ascension and declination, respectively; pm: ok = proper motion applied, no = no proper motion applied; catalogue cross-identification (ct) = uc (UCAC2), 2m (2MASS), fs (field star); $E_{\alpha *}$ and $E_{\delta}$: uncertainties (mas) in right ascension and declination. A value of 9999 means that there was no estimation of the respective uncertainty; $\mu_{\alpha *}$ and $\mu_{\delta}$: proper motions in right ascension and declination, respectively (mas/year).
\label{Tab: occ-list}
\end{table*}

\begin{figure*}
\begin{centering}
\includegraphics[scale=0.4]{figures/Pasiphae_2016-04-09T03:58:19.png}   
\caption{Occultation map for Himalia regarding to the fifth event sampled in Table \ref{Tab: occ-list}}
\label{Fig: ocultacao}
\end{centering}
\end{figure*}

@@

The candidate stars was searched in the UCAC4 catalogue, except for the candidates in 2015 and 2016 for Triton and Nereid. In this case, we used the WFI catalogue that was generated from observations made with ESO2p2/WFI CCD mosaic that covered the path of Neptune in the sky-plane up to 2016 (see Sec. \ref{Sec: predictions}). From this, a total of \textcolor{red}{588} events were foreseen.

>>>>

\begin{figure*}
\subfigure{\includegraphics[width=8.8cm]{figures/Himalia_resid.eps}   \label{Fig: residuals-Himalia}}
\subfigure{\includegraphics[width=8.8cm]{figures/Carme_resid.eps}  \label{Fig: residuals-Carme}}
\caption{Residuals of Himalia and Carme \label{Fig: residuals}}
\end{figure*}

@@

\begin{table*}
\caption{\label{Tab: sample-cds} Stellar occultation sampled predictions for Pasiphae}
\begin{centering}
\begin{tabular}{cccrcccrcrr}
\hline
\hline
d m Year~~~~h~~m~~~s & RA~~~(ICRS)~~~Dec & C/A & P/A & $\nu$ & {\it D} & R* & $\lambda$ & LST & $\mu_{\alpha*}$ & $\mu_{\delta}$ \tabularnewline
\hline
% & \multicolumn{2}{c}{Mean errors} & Nr & Nr &  UCAC4       \tabularnewline
09 04 2016 03:58:19. & 11 14 36.7707 +07 39 20.7610 & 1.003 &  17.9 & -12.88 &  4.54 & 14.9 & 271. & 22:03 &  12. & -33. \tabularnewline 
13 06 2016 00:16:12. & 11 12 48.5020 +07 06 43.3520 & 0.661 &  30.0 & +14.32 &  5.50 & 13.9 & 262. & 17:45 &  -1. &   1. \tabularnewline 
27 06 2016 13:56:09. & 11 18 03.4160 +06 23 45.1940 & 1.707 &  28.0 & +20.29 &  5.74 & 11.7 &  44. & 16:53 &   4. & -10. \tabularnewline 
18 07 2016 15:07:24. & 11 28 15.5076 +05 05 31.8060 & 0.942 &  26.7 & +27.80 &  6.05 & 14.0 &   8. & 15:40 &   4. &   4. \tabularnewline 
22 07 2016 16:15:07. & 11 30 30.4310 +04 48 43.4340 & 0.644 & 206.5 & +29.04 &  6.11 & 14.6 & 348. & 15:27 &  23. & -24. \tabularnewline 
24 07 2016 01:37:34. & 11 31 17.8471 +04 42 49.0540 & 0.029 & 206.6 & +29.46 &  6.12 & 15.1 & 206. & 15:22 &   2. &  -8. \tabularnewline 
24 07 2016 17:37:18. & 11 31 40.7472 +04 39 57.5060 & 0.840 &  26.5 & +29.66 &  6.13 & 14.9 & 326. & 15:20 & -11. &  -1. \tabularnewline 
\hline
\end{tabular}
\par\end{centering}
\textbf{Notes}. Entries included: day of the year and UTC time of the prediction; right ascension and declination of the occulted star - in the original table; C/A: the geocentric closest approach, in arcseconds; P/A: the planet position angle with respect to the occulted star at C/A, in degrees; $\nu$: velocity in plane of sky, in km s$^{-1}$: positive = prograde, negative = retrograde; {\it D}: planet range to Earth, in AU; R*: normalized magnitude to a common shadow velocity of 20 km s$^{-1}$ by the relationship $\textrm{R}* = \textrm{R}_{\textrm{actual}} + 2.5 \times \log 10 \left(\frac{\textrm{velocity}} {20 \textrm{km}\, \textrm{s}^{-1}} \right)$; $\lambda$: east longitude of subplanet point in degrees, positive towards east; LST: UT + $\lambda$: local solar time at subplanet point, hh:mm; $\mu_{\alpha *}$ and $\mu_{\delta}$: proper motions in right ascension and declination, respectively (mas/year).
\label{Tab: occ-list}
\end{table*}

\begin{figure*}
\begin{centering}
\includegraphics[scale=0.4]{figures/Pasiphae_2016-04-09T03:58:19.png}   
\caption{Occultation map for Himalia regarding to the first event sampled in Table \ref{Tab: occ-list}}
\label{Fig: ocultacao}
\end{centering}
\end{figure*}

@@

The candidate stars was searched in the UCAC4 catalogue, except for the candidates in 2015 and 2016 for Triton and Nereid. In this case, we used the WFI catalogue that was generated from observations made with ESO2p2/WFI CCD mosaic that covered the path of Neptune in the sky-plane up to 2016 (see Sec. \ref{Sec: predictions}). From this, a total of 687 events were foreseen.
